On the Synchronization of Computational RFIDs

### 2018-07-10 TMC-2017-11-0695.R1-main.tex
Henko Aantjes bio added (first version), front footer with addressess changed, revisions of bios

\author{Kas{\i}m~Sinan~Y{\i}ld{\i}r{\i}m, 
	Henko~Aantjes, 
	Przemys{\l}a~Pawe{\l}czak~\IEEEmembership{Member,~IEEE,} 
	and~Amjad~Yousef~Majid
	%
	\IEEEcompsocitemizethanks{
		\IEEEcompsocthanksitem A preliminary version of this article was presented at the HLPC 2016 Workshop, Atlanta, GA, USA, April 2, 2016~\cite{hlpc2016}.
		\IEEEcompsocthanksitem The authors are with the Embedded Software Group, Delft University of Technology, Mekelweg 4, 2628 CD Delft, The Netherlands (e-mail: \{k.s.yildirim, p.pawelczak, a.y.majid\}@tudelft.nl, h.aantjes@student.tudelft.nl). 
		\IEEEcompsocthanksitem Kas{\i}m Sinan Y{\i}ld{\i}r{\i}m is also with the Computer Engineering Department of Ege University, Izmir, Turkey.
	}
%	\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}
}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{author_photos/ksy.jpeg}}]{Kas{\i}m Sinan Y{\i}ld{\i}r{\i}m}
received his Ph.D. degree in Computer Engineering from Ege University 
in 2012. He was a visiting scholar at the Department of Information Engineering, University of Padova in 2013. Between 2015-2017, he was a post-doctoral researcher at Embedded Software Group, Delft University of Technology. Currently, he is an assistant professor at the Department of Computer Engineering, Ege University and also a research affiliate with the Embedded Software Group at Delft University of Technology. His research interests are embedded systems and software, distributed algorithms,  wireless sensor networks, energy harvesting systems and computational RFIDs.
\end{IEEEbiography}

% if you will not have a photo at all:
\begin{IEEEbiographynophoto}{Henko Aantjes}
Biography text here.
\end{IEEEbiographynophoto}
%
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{author_photos/przemek.jpg}}]{}
Biography text here.	
\end{IEEEbiography}
%
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{author_photos/amjad.jpg}}]{Amjad Yousef Majid}
Biography text here.
\end{IEEEbiography}
%
% insert where needed to balance the two columns on the last page with
% biographies
%\newpage

>>>>

\author{Kas{\i}m~Sinan~Y{\i}ld{\i}r{\i}m, 
	Henko~Aantjes, 
	Przemys{\l}aw~Pawe{\l}czak~\IEEEmembership{Member,~IEEE,} 
	and~Amjad~Yousef~Majid
	%
	\IEEEcompsocitemizethanks{
		\IEEEcompsocthanksitem A preliminary version of this article was presented at the HLPC 2016 Workshop, Atlanta, GA, USA, April 2, 2016~\cite{hlpc2016}.
		\IEEEcompsocthanksitem Kas{\i}m Sinan Y{\i}ld{\i}r{\i}m, Przemys{\l}aw Pawe{\l}czak and Amjad Yousef Majid are with the Embedded Software Group, Delft University of Technology, Mekelweg 4, 2628 CD Delft, The Netherlands (e-mail: \{k.s.yildirim, p.pawelczak, a.y.majid\}@tudelft.nl).
		\IEEEcompsocthanksitem Henko Aantjes is with the Brighsight BV, Brassersplein 2, 2612\,CT, Delft, The Netherlands (e-mail: aantjes@brightsight.com)
		\IEEEcompsocthanksitem Kas{\i}m Sinan Y{\i}ld{\i}r{\i}m is also affilated with the Computer Engineering Department of Ege University, Izmir, Turkey.
	}
%	\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}
}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{author_photos/ksy.jpeg}}]{Kas{\i}m Sinan Y{\i}ld{\i}r{\i}m}
received his Ph.D. degree in Computer Engineering from Ege University in 2012. He was a visiting scholar at the Department of Information Engineering, University of Padova in 2013. Between 2015 and 2017, he was a post-doctoral researcher at Embedded Software Group, Delft University of Technology. Currently, he is an assistant professor at the Department of Computer Engineering, Ege University and also a research affiliate with the Embedded Software Group at Delft University of Technology. His research interests are embedded systems and software, distributed algorithms, wireless sensor networks, energy harvesting systems and computational RFIDs.
\end{IEEEbiography}

% if you will not have a photo at all:
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{author_photos/henko.jpg}}]{Henko Aantjes}
Henko Aantjes received his MSc degree in 201X. Currently he is a security evaluator at Brightsight BV, Delft, The Netherlands. His research interests include computational RFIDs, secure computation, and contactless payments.
\end{IEEEbiography}
%
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{author_photos/przemek.jpg}}]{}
Biography text here.	
\end{IEEEbiography}
%
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{author_photos/amjad.jpg}}]{Amjad Yousef Majid}
obtained his MSc degree in Computer Science from Delft University of Technology in 2015. Currently, he is a PhD candidate at the Embedded Software Group at Delft University of Technology. His research focuses on intermittent software architecture, (computational) RFIDs, backscatter technology, and wireless sensor networks.
\end{IEEEbiography}
%
% insert where needed to balance the two columns on the last page with
% biographies
%\newpage
